Environmental stress affects niche breadth in plant-pollinator communities

### 2019-11-10 paper/supp-info.Rmd
Draft reference table

```{r tab-manual-name-corrections}
loadd(spp, manual_name_corrections)
manual_name_corrections %>%
  inner_join(spp, by = c("queried_sp_name" = "sp_name")) %>%
  distinct(queried_sp_name, sp_name, guild) %>%
  filter(!is.na(sp_name)) %>%
  arrange(guild, queried_sp_name, sp_name) %>%
  mutate(sp_name = tidyr::replace_na(sp_name, "no replacement found"), 
         sp_name = kableExtra::cell_spec(sp_name, italic = TRUE), 
         guild = if_else(guild == "pla", "plant", "pollinator")) %>%
  knitr::kable(caption = "Manually corrected canonnical names. More than one correct name have been included when an accepted/valid synonym the cannonical name exists.", 
               col.names = c("incorrect name", "corrected name", "guild"),
               booktabs = TRUE, 
               escape = F) %>%
  kableExtra::kable_styling(font_size = 8) %>%
  kableExtra::collapse_rows(1, latex_hline = "none", valign = "top")
```

@@

>>>>

```{r tab-manual-name-corrections}
loadd(spp, manual_name_corrections)
manual_name_corrections %>%
  inner_join(spp, by = c("queried_sp_name" = "sp_name")) %>%
  distinct(queried_sp_name, sp_name, guild) %>%
  filter(!is.na(sp_name)) %>%
  arrange(guild, queried_sp_name, sp_name) %>%
  mutate(sp_name = tidyr::replace_na(sp_name, "no replacement found"), 
         sp_name = kableExtra::cell_spec(sp_name, 
                                         format = "latex", 
                                         italic = TRUE), 
         guild = if_else(guild == "pla", "plant", "pollinator")) %>%
  knitr::kable(format = "latex", 
               caption = "Manually corrected canonnical names. More than one correct name have been included when an accepted/valid synonym the cannonical name exists.", 
               col.names = c("incorrect name", "corrected name", "guild"),
               booktabs = TRUE, 
               escape = F) %>%
  kableExtra::kable_styling(font_size = 8) %>%
  kableExtra::collapse_rows(1, latex_hline = "none", valign = "top")
```

```{r}
loadd(recoded_interactions, int_metadata)

n_sp_ids <- recoded_interactions %>%
  select(-loc_id) %>%
  purrr::map(n_distinct) %>%
  unlist() %>% sum()

n_names_in_multiple_references_after <- recoded_interactions %>%
  tidyr::gather(key = "guild", "sp_id", pla_id, ani_id) %>%
  left_join(study_per_location, by = "loc_id") %>%
  group_by(sp_id) %>%
  summarise(n_ref = n_distinct(reference)) %>%
  filter(n_ref > 1) %$%
  n_distinct(sp_id)

data_sources_mult_nets <- int_metadata %>%
  group_by(loc_id) %>%
  summarise(n_nets = n_distinct(net_name)) %>%
  filter(n_nets > 1)

n_data_sources_mult_nets <- nrow(data_sources_mult_nets)
```

This cleaning process allowed us to match further `r n_sp_names - n_sp_ids` names across data sources and, by doing so, identify another `r n_names_in_multiple_references_after - n_names_in_multiple_references_orig` species that were present in more than one study. 
The process also allowed us to identify `r numbers2words(length(problematic_networks))` problematic data sources in which some names were included as both plants and pollinators. 
These data sources were removed from further analysis. 
In `r numbers2words(n_data_sources_mult_nets)` of our data sources interaction data was recorded at multiple points in time. 
When this was the case, we combined interaction data into one single interaction network.

```{r tab-studies, eval = F}
loadd(int_metadata)
loadd(interaction_citations)

simple_metadata <- int_metadata %>%
  filter(stringr::str_detect(reference, pattern = "unpubl", negate = TRUE)) %>%
  group_by(loc_id) %>%
  summarise(location = paste0(round(mean(lon), 2), ", ", 
                              round(mean(lat), 2)), 
            name = first(loc_name), 
            ref = first(reference)) %>%
  # first word in the references is the main author (usually)
  mutate(first_author = stringr::str_extract(ref, "^\\w+"), 
         # the first number of four digits is the year
         year = stringr::str_extract(ref, "[0-9]{4}"), 
         key = paste(tolower(first_author), year, sep = "_")) %>%
  select(-first_author, -year)

interaction_citations %>%
  mutate(first_author = stringr::str_extract(BIBTEXKEY, "[^_-]+"), 
         year = stringr::str_extract(BIBTEXKEY, "[0-9]{4}"), 
         key = paste(tolower(first_author), year, sep = "_"), 
         bibtex_key = BIBTEXKEY) %>%
  select(bibtex_key, key) %>%
  fuzzyjoin::stringdist_full_join(simple_metadata, 
                                  by = c(key = "key"), 
                                  max_dist = 6, 
                                  distance_col = "dist") %>% 
  group_by(key.y) %>%
  filter(dist == min(dist)) %>%
  ungroup() %>%
  select(location, name, bibtex_key) %>%
  mutate(bibtex_key = paste0("@", bibtex_key, "")) %>%
  knitr::kable(format = "markdown", 
               escape = F, 
               booktabs = T, 
               col.names = c("coordinates", "site", "reference"),
               caption = "Sites included in this study")
  kableExtra::kable_styling(font_size = 8)
```

@@

# Supplementary references
